The microbiota of the proximal and distal human colon

### 2017-08-23 submission/manuscript.Rmd
starting working on feature reduction

The _Fusobacterium_ species _nucleatum_ and _varium_ have been commonly isolated from mucosal biopsies of patients with IBD @Lee2016. Laboratory experiments with these isolates have shown that disease-isolated _F. nucleatum_ are more invasive and stimulate more TNF-\alpha production than strains from healthy individuals @Strauss2011, suggesting the bacteria may increase inflammation in the gut as well @Dharmani2011. _F. varium_ isolated from UC patients caused colonic ulcers in an experimental mouse model @Ohkusa2003. _F. varium_ was only detected in three of our study participants and two of those samples were isolated form the proximal mucosa (Figure 6B).  _F. varium_ is most commonly isolated from UC patient biopsies from the ileum or cecum @Ohkusa2002, suggesting this species may exhibit preference for the different environmental conditions of these gastrointestinal sites. Further work will assess how gut environment may select for species which may then cause localized disease.

@@

#### Statistical analysis
Differences in community membership at the phyla level were tested using the analysis of molecular variance (AMOVA) metric in mothur. Differences in thetaYC distances by location were tested using the Wilcoxon rank-sum test adjusted for multiple comparisons using the Benjamini-Hochberg procedure.

>>>>

The _Fusobacterium_ species _nucleatum_ and _varium_ have been commonly isolated from mucosal biopsies of patients with IBD @Lee2016. Laboratory experiments with these isolates have shown that disease-isolated _F. nucleatum_ are more invasive and stimulate more TNF-$\alpha$ production than strains from healthy individuals @Strauss2011, suggesting the bacteria may increase inflammation in the gut as well @Dharmani2011. _F. varium_ isolated from UC patients caused colonic ulcers in an experimental mouse model @Ohkusa2003. _F. varium_ was only detected in three of our study participants and two of those samples were isolated form the proximal mucosa (Figure 6B).  _F. varium_ is most commonly isolated from UC patient biopsies from the ileum or cecum @Ohkusa2002, suggesting this species may exhibit preference for the different environmental conditions of these gastrointestinal sites. Further work will assess how gut environment may select for species which may then cause localized disease.

@@

#### Statistical analysis
Differences in community membership at the phyla level were tested using the analysis of molecular variance (AMOVA) metric in mothur. Differences in $\theta$<sub>YC</sub> distances by location were tested using the Wilcoxon rank-sum test adjusted for multiple comparisons using the Benjamini-Hochberg procedure.
